Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-07 ms/SI.Rmd
update

val <- yaml::yaml.load_file("../values.yml")
```

@@

```{r}
library(jsonlite)
site <- fromJSON("../data/site_info.json")
site |>
  kable(format = "html") |>
  kable_styling()
```

@@

@@

>>>>

# for dependency
targets::tar_load(yml)
#  for non-targets
# val <- yaml::yaml.load_file("../values.yml")
val <- yaml::yaml.load_file("values.yml")
```

@@

```{r, echo=TRUE}
library(jsonlite)
# for dependency
targets::tar_load(site_info)
#site <- fromJSON("../data/site_info.json")
site <- fromJSON("data/site_info.json")
site |>
  kable(format = "html") |>
  kable_styling()
```

@@

```{r, incude=FALSE}
targets::tar_load(coef_sp_punch1_add_plot)
```

@@

```{r, include=FALSE}
targets::tar_load(lma_ld_png)
```
